Study of the numerical solution of X-Modes equations around the hybrid resonnance

### 2015-01-20 report/intro.tex
adding first batch of refs

 As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
 \begin{align}
-\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
\mu_0 \partial_t \Hbf + \curl\, \E = 0
\end{align}
coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, taking into account the friction between electron and ions
\be
m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
\ee
Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current, 
$\ubf_e$ is the velocity of electrons and $B_0$ is the background magnetic field.  
We denote by $e<0$ the value of the charge of electrons and by $m_e$ the electron mass.
Assuming that $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, we obtain the following system of equations 
\begin{align}
\label{eq:main_model}
\begin{split}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{split}
\end{align}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. 
In this work we look at a simplification of this model obtained after 
the Fourier transform in $y$. Denoting by $\theta$ a corresponding Fourier variable, the model (\ref{eq:main_model}) can be rewritten as follows
\begin{align}
\label{eq:main_model_theta}
\begin{split}
\epsilon_0\partial_t E_{x}-\theta H=-eN_e u_x,\nonumber\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
\mu_0\partial_t H+\partial_x E_y-\theta E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.
\end{split}
\end{align}
The energy of this system can be expressed as \cite{}
\begin{align*}

\end{align*}
From this it can be seen that when the term $\nu=0$, the electron density $N_e(x)$ vanishes and in plasma there occurs a resonance \cite{Stix}, 
which was recently investigated in \cite{}, in particular, it was shown that the electric field $E_x$ in this case is no longer square 
integrable, and explicit estimates on the behaviour of the solutions of (\ref{eq:main_model_theta}) were given.

Thus, the goal of this article is two-fold. 
First, following (\ref{}), we investigate the finite element approximation of the 
problem (\ref{eq:main_model_theta}) written in the frequency domain:
\begin{align*}

\end{align*}
We prove the well-posedness of this problem for $\nu>0$ in Section \ref{} and 
demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity of the solution fairly well (Section \ref{}). 
Second, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization (\ref{eq:main_model_theta}), suggested in \cite{}. We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, i.e.
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.

>>>>

As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
\begin{align}
-\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
\mu_0 \partial_t \Hbf + \curl\, \E = 0
\end{align}
coupled with a linear current in two dimensions $\J = eN_e \ubf_e$, taking into account the friction between electron and ions
\be
m_e \partial_t \ubf_e =e (\E +\ubf_e \nabla B_0) -m_e \nu \ubf_e. \label{eq:electronmove}
\ee
Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current, 
$\ubf_e$ is the velocity of electrons and $B_0$ is the background magnetic field.  
We denote by $e<0$ the value of the charge of electrons and by $m_e$ the electron mass.
Assuming that $\mathbf{B}_0=\left(0,\; 0,\; B_0\right)$, we obtain the following system of equations 
\begin{align}
\label{eq:main_model}
\begin{split}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{split}
\end{align}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. 
In this work we look at a simplification of this model obtained after 
the Fourier transform in $y$. Denoting by $\theta$ a corresponding Fourier variable, the model (\ref{eq:main_model}) can be rewritten as follows
\begin{align}
\label{eq:main_model_theta}
\begin{split}
\epsilon_0\partial_t E_{x}-\theta H=-eN_e u_x,\nonumber\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\nonumber\\
\mu_0\partial_t H+\partial_x E_y-\theta E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\nonumber\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y.
\end{split}
\end{align}
The energy of this system in a domain $\Omega$ can be expressed as \cite{stable_yee_plasma_current}
\begin{align*}
{\mathcal E}(t)= \int_\Omega \frac{1}{2\mu_0}|U(t,\x)|^2\mathrm{d}\x =\int_\Omega \left(
\frac{\epsilon_0 |\E(t,\x)|^2}{2}+\frac{ |\B(t,\x)|^2}{2\mu_0}+\frac{m_e|\J (t,\x)|}{2|e|N_e(\x)} \mathrm{d}\x.
\right)
\end{align*}

From this it can be seen that when the term $\nu=0$ and the electron density $N_e(x)$ vanishes, 
in plasma there occurs a resonance~\cite{Stix}. Mathematically, this effect was recently investigated in \textcolor{red}{citationtofix}\cite{}, 
in particular, it was shown that the electric field $E_x$ in this case is no longer square 
integrable, and explicit estimates on the behaviour of the solutions of (\ref{eq:main_model_theta}) were given.

Thus, the goal of this article is two-fold. 
First, following (\textcolor{red}{reftofix}\ref{}), we investigate the finite element approximation of the 
problem (\ref{eq:main_model_theta}) written in the frequency domain:
\begin{align*}
\end{align*}
We prove the well-posedness of this problem for $\nu>0$ in Section \textcolor{red}{reftofix}\ref{} and 
demonstrate that the use of higher-order (P1) finite elements allows to approximate the singularity of the solution fairly well (Section \textcolor{red}{reftofix}\ref{}). 
Second, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization (\ref{eq:main_model_theta}), suggested in \textcolor{red}{citationtofix}\cite{}. We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{i\omega t}$, computed in the frequency domain, for $\nu\rightarrow 0$, i.e.
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.

### 2015-01-20 report/proc.tex
small fixes decided at the phone
changed the formulation of the theorem
experiments adding+ formatting has changed a bit
modified intro a bit
intro upd #2
adding first batch of refs

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a template file for Proccedings 
%
% Copy it to a new file with a new name and use it as the basis
% for your article
%
%%%%%%%%%%%%%%%%%%%%%%%%   EDP Sciences  %%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[proc]{edpsmath}
%
%\usepackage{amsfonts,graphicx,amssymb}%amsfonts pour les \mathbb
%\usepackage{amsmath,amsthm,amssymb}
%%%%%%%%%%%%%--PREAMBLE--%%%%%%%%%%%%%%%%%%
%%-----------------------------
%%         ...........
%%         your macros
\usepackage[frenchb,english]{babel}
\usepackage{macros}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{hyperref}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\definecolor{blue}{rgb}{0.30,0.8,1}
\definecolor{red}{rgb}{1,0.3,0.3}
\usetikzlibrary{positioning,shapes,shadows,arrows}

@@

%%-----------------------------
%%      the top matter
%%-----------------------------
\title{Study of the
	numerical solution of X-Modes equations around the hybrid resonnance} %\thanks{...}\thanks{...}% At most 5 thanks
%
\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
\author{Bruno Depsr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
\author{Lise-Marie Imbert}\address{Courant Institute of Mathematical Sciences, New York University}
\author{Maryna Kachanovska}\address{UMA, ENSTA, Paris}

@@

\input{intro}
\input{equations}
\input{numerics}
\input{timedomain}
\input{absorption}
\begin{thebibliography}{99}
\bibitem{stable_yee_plasma_current} F. da Silva, M. Campos Pinto, B. Despres, S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
2014
\end{thebibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a template file for Proccedings 
%
% Copy it to a new file with a new name and use it as the basis
% for your article
%
%%%%%%%%%%%%%%%%%%%%%%%%   EDP Sciences  %%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[proc]{edpsmath}
%
%\usepackage{amsfonts,graphicx,amssymb}%amsfonts pour les \mathbb
%\usepackage{amsmath,amsthm,amssymb}
%%%%%%%%%%%%%--PREAMBLE--%%%%%%%%%%%%%%%%%%
%%-----------------------------
%%         ...........
%%         your macros
\usepackage[frenchb,english]{babel}
\usepackage{macros}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsfonts,amssymb,amsthm,epsfig,epstopdf,array}
\usepackage{tikz}
\usepackage{caption}
\usepackage{pgfplots}
\usepackage{ulem}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{hyperref}
%\usepackage{diagbox}
\newenvironment{remark}[1][Remark]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\definecolor{blue}{rgb}{0.30,0.8,1}
\definecolor{red}{rgb}{1,0.3,0.3}
\usetikzlibrary{positioning,shapes,shadows,arrows}

@@

%%-----------------------------
%%      the top matter
%%-----------------------------
\title{Study of the
	numerical solution of X-Modes equations around the hybrid resonnance} %\thanks{...}\thanks{...}% At most 5 thanks
%
\author{C\'eline Caldini-Queiros}\address{Max Planck Institute für PlasmaPhysik, Garching bei Muenchen}
\author{Bruno Depsr\'es}\address{Laboratoire Jacques-Louis Lions, University PARIS 6}
\author{Lise-Marie Imbert-Gérard}\address{Courant Institute of Mathematical Sciences, New York University}
\author{Maryna Kachanovska}\address{POEMS, INRIA, ENSTA ParisTech, Paris}

@@

\input{intro}
\input{equations}
\input{numerics}
\input{timedomain}
%\input{absorption}
\begin{thebibliography}{99}
\bibitem{stable_yee_plasma_current} F. da Silva M. Campos Pinto, B. Despres and S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
2014
\bibitem{Depres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
\bibitem{LMIG_thesis} Imbert-Gérard, L. M. (2013). Analyse mathématique et numérique de problèmes d'ondes apparaissant dans les plasmas magnétiques (Doctoral dissertation, Université Pierre et Marie Curie-Paris VI).
\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
\end{thebibliography}
